Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-01-28 hscc2017/paper.tex
wording

Let $\hat{C}(z)$ be the digital controller transfer function
represented using this FWL with integer size $I$ and fractional size~$F$;
$I$ affects the representation range and is set to avoid overflows, 
while $F$ affects the precision and the truncation process after the 
arithmetic operations. These variables are chosen depending on 
hardware features.  In general-purpose processors and
DSP's, $I$ is minimized to avoid overflows and $F$ is employed for the
remaining bit representation. Other flexible hardware structures
(e.g., FPGAs) allow the design of $F$ and $I$, which affects directly
the number of logical gates.

We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F
\rangle$
%
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
%
and assume that there exists a function
$\mathit{FWL}_n[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
which applies the FWL effects to a polynomial, with an equivalent $\mathit{FWL}_{n,m}[\cdot]:\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that applies the same effect to a ratio of polynomials, where
$\mathcal{P}^{n}$ is the
space of polynomials of $n$-th order, $\mathcal{P}^{n}\langle I,F
\rangle$ is the space of polynomials with coefficients in
$\mathbb{R}\langle I,F \rangle$, and $\mathcal{P}^{n,m}$,  $\mathcal{P}^{n,m}\langle I,F
\rangle$ are their rational equivalent.

>>>>

Let $\hat{C}(z)$ be the digital controller transfer function represented
using this FWL with integer size $I$ and fractional size~$F$; $I$ affects
the range of the representation and is set to avoid overflows, while $F$
affects the precision and the truncation after arithmetic operations.
We shall denote the FWL domain of the coefficients by $\mathbb{R}\langle I,F
\rangle$
%
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
%
and assume that there exists a function
$\mathit{FWL}_n[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
which applies the FWL effects to a polynomial, with an equivalent $\mathit{FWL}_{n,m}[\cdot]:\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that applies the same effect to a ratio of polynomials, where
$\mathcal{P}^{n}$ is the
space of polynomials of $n$-th order, $\mathcal{P}^{n}\langle I,F
\rangle$ is the space of polynomials with coefficients in
$\mathbb{R}\langle I,F \rangle$, and $\mathcal{P}^{n,m}$,  $\mathcal{P}^{n,m}\langle I,F
\rangle$ are their rational equivalent.
